---
title: "7.3.73"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 7.3.73

An ethanol railroad tariff is a fee charged for shipments of ethanol on public railroads. An agricultural association publishes tariff rates for​ railroad-car shipments of ethanol. Assuming that the standard deviation of such tariff rates is ​$
1300​,determine the probability that the mean tariff rate of 350 randomly selected​ railroad-car shipments of ethanol will be within ​$110 of the mean tariff rate of all​ railroad-car shipments of ethanol. Interpret your answer in terms of sampling error.
<br/>
<hr/>

**The probability is (Round to three decimal places as needed)**

The sample size n = 350 since there are 350 tariff randomly selected.

Since the sample size is more than 30, the variable is normally distributed followed by the central limit theorem.

Population standard deviation $\sigma=1300$

```{r}
n = 350  
sigma = 1300
```
First we need to find sample standard deviation by using the formula $\sigma_{\bar{x}}=\frac{\sigma}{\sqrt{n}}$
```{r}
s = sigma/sqrt(n)
s
```
Next, we need to find the test statistic by using the formula $z=\frac{x-\mu}{\sigma}$

Since our estimated points are within 110 of the mean, so $x = \mu \pm 110 $
. It follows that $z=\frac{\pm110}{\sigma_{\bar{x}}}$
```{r}
110 / s
-110/ s
```
We can get the area between two estimated points by using pnorm()
```{r}
pnorm(110 / s) - pnorm(-110 / s) 
```
Round to three decimal places
```{r}
round(pnorm(110 / s) - pnorm(-110 / s) , 3)
```
<hr />

<hr />
**Hope that helps!**