---
title: "14.2.63"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 14.2.63

An instructor asked a random sample of eight students to record their study times at the beginning of a course. She then made a table for total hours studied​ (x) over 2 weeks and test score​ (y) at the end of the 2 weeks. The table is given below. Complete parts​ (a) through​ (f).

$\sum x = 396, \sum y = 2362, \sum xy = 118330, \sum x^2 = 19870$
<br/>
<hr/>
**(a). Find the regression equation for the data points.**

First we need to get the data from the question. (We can import it from Excel)
```{r}
x<- c(12, 15, 11, 19, 8, 17, 16, 23)
y<- c(95, 76, 80, 75, 90, 75, 83, 75)
```
<hr/>
From formula sheet

$S_{xx}=\sum(x_i-\bar{x})^2=\sum x_i^2-(\sum x_i)^2/n$

$S_{xy}=\sum(x_i-\bar{x})(y_i-\bar{y})=\sum x_iy_i-(\sum x_i)(\sum y_i)/n$

$S_{yy}=\sum(y_i-\bar{y})^2=\sum y_i^2-(\sum y_i)^2/n$

<hr/> 
Regression equation: $\hat{y} = b_0 +b_1x$ where 

$b_1=\frac{S_{xy}}{S_{xx}}$ and

$b_0 = \frac{1}{n}(\sum y_i-b_1\sum x_i)=\bar{y} - b_1\bar{x}$

<hr/>
**Names of variables**

$S_{xx}: Sxx$

$S_{xy}: Sxy$

$S_{yy}: Syy$

<hr/>
**First approach, we find linear regression line by using the formula**

**1.1 we find $S_{xy}, S_{xx}, S_{yy}$ without finding $\bar x, \bar y$**

```{r}
n = length(x)
```

Find $S_{xy}, S_{xx}, S_{yy}$
```{r}
Syy = sum(y*y) - sum(y)^2/n
Sxx = sum(x*x) - sum(x)^2/n
Sxy = sum(x*y) - sum(x) * sum(y) /n
```

```{r}
Sxx
Sxy
Syy
```

<hr/>
**1.2 finding $S_{xy}, S_{xx}, S_{yy}$ using $\bar x, \bar y$ **

```{r}
Sxx = sum((x-mean(x))^2)
Sxy = sum((x-mean(x))*(y-mean(y)))
Syy = sum((y-mean(y))^2)
```

```{r}
Sxx
Sxy
Syy
```
<hr/>

To find $b_0$ and $b_1$ in the regression equation: $\hat{y} = b_0 +b_1x$, we run
```{r}
b1 = Sxy / Sxx
b1
```

```{r}
b0 = mean(y) - b1 * mean(x)
b0
```
Round to two decimal places
```{r}
round(b1, 2)
round(b0, 2)
```

**Second approach, we find linear regression line by using lm() in R**
```{r}
lm(y~x)
```
In case that R does not give enough accuracy, we use print()
```{r}
print(lm(y~x), 15)
```

**Since we have two approaches here, we could do both to double check our answers before submiting.**

**(b). Graph the regression equation and the data points.**

We draw a graph by using plot() and abline(). Abline() takes 2 arguments y-intercept ($b_0$) and slope ($b_1$)
```{r}
plot(x,y)
abline(b0, b1)
```

<hr/>
**(c) Describe the apparent relationship between the two variables.**

Since we have negative slope, when x increasess y tends to decrease which means Test Score tends to decrease as Hours Studied increases

<hr/>
**(d) Identify the predictor and response variables.**

The predictor variable is x and the response variable is y.

So the predictor variable is Hours Studied and the response variable is Test Score.

<hr/>
**(e) Identify outliers and potential influential observations.**

"An outlier is an observation that lies outside the overall pattern of the data. In the context of regression​ analysis, an outlier is a data point that lies far from the regression line relative to the other data points. An influential observation is a data point whose removal causes the regression equation and line to change considerably."

We can tell from the graph that there is no outlier or potential influential observation.
<hr/>
**(f). Predict the score for a student that studies for 15hours.**

Since the regression equaation in part a requires rounding the answer to two decimal places

```{r}
b0 = round(b0, 2)
b1 = round(b1, 2)
```

```{r}
b0
```

```{r}
b1
```

To find predicted score for a student that studies for 15 hours, we run
```{r}
b0 + 15 * b1
```
Round to the nearest whole number as needed
```{r}
ceiling(b0 + 15 * b1)
```
<hr/>
**Hope that helps!**
