---
title: "10.5.157"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 10.5.157

A researcher randomly selects 6 fathers who have adult sons and records the​ fathers' and​ sons' heights to obtain the data shown in the table below. Test the claim that sons are taller than their fathers at the $\alpha =$ 0.10
level of significance. The normal probability plot and boxplot indicate that the differences are approximately normally distributed with no outliers so the use of a paired​ t-test is reasonable.

<br/>

**What are the hypotheses for the​ t-test? Note that population 1 is fathers and population 2 is sons.**

Since test the claim that sons are taller than their fathers, we have left-tailed test

$H_0:\mu_1 = \mu_2$

$H_a:\mu_1 < \mu_2$

First, we need to get the data from the question. (We could import the data from Excel)
```{r}
father <- c(66.6, 74.5, 68.2, 66.6, 73.7, 74.9)
son <- c(68.9, 76.0, 67.6, 64.1, 73.0, 79.4)
```
<hr />
**Use population 1 minus population 2 as the difference.**

We store difference between father and son in variable difference and run test statistic.
Since $\alpha = .10$ we have confidence level = .9 
**First approach use t.test()**
```{r}
difference = father - son
t.test(difference, conf.level = .9, alternative = "less")
```
Round to 3 decimal places
```{r}
print(t.test(difference, conf.level = .9, alternative = "less"),5)
```
Since we have 6 pairs of data, our degree of freedom is 6 - 1 = 5 and we have left-tailed test with $\alpha = .1$, the area to the left of  critical value = $\alpha$ 
```{r}
round(qt(.1, 5), 3)
```

Since the test statistic value t = -0.732 is larger than the critical value $t_{\alpha} = -1.476$, we do not have enough evidence to reject hypothesis.
<hr/>
**Second appraach to find test statistic, we can use formula**
$t=\frac{\bar d}{\frac{s_d}{\sqrt{n}}}$
```{r}
n = 6
mean(difference)/(sd(difference)/sqrt(n))
```
Round to 3 decimal places
```{r}
round(mean(difference)/(sd(difference)/sqrt(n)),3)
```
**It is good to know both approaches so we could check the answer from t.test() in R**
<hr/>
**Hope that helps!**