---
title: "8.2.63"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 8.2.63

A sample​ mean, sample​ size, population standard​ deviation, and confidence level are provided. Use this information to complete parts​ (a) through​ (c) below.

$\bar{x}=24, n=37, \sigma=3, confidence level = 95%$
<br/>

**(a). Use the​ one-mean z-interval procedure to find a confidence interval for the mean of the population from which the sample was drawn.**


First, we need to get the data from the question
```{r}
x = 24
n = 37
sigma = 3
alpha = .05
```
<hr />
**We do not use the empirical rule like in question 8.1.11**
<hr/>
To find confidence interval, we use formulas $\bar{x} \pm z_{\frac{\alpha}{2}}.\frac{\sigma}{\sqrt{n}}$

First we find $z_{\frac{\alpha}{2}}$ by using qnorm()
```{r}
zalpha2 = abs(qnorm(alpha/2))
zalpha2
```
To find 95% confidence interval, we run
```{r}
x - zalpha2 * sigma/sqrt(n)
x + zalpha2 * sigma/sqrt(n)
```
<hr/>
Round to one decimal places as needed
```{r}
round(x - zalpha2 * sigma/sqrt(n), 1)
round(x + zalpha2 * sigma/sqrt(n), 1)
```
**(b).Obtain the margin of error by taking half the length of the confidence interval.What is the length of the confidence​ interval?**

Length of confidence interval
```{r}
round(x + zalpha2 * sigma/sqrt(n), 1)-round(x - zalpha2 * sigma/sqrt(n), 1)
```
Margin of error = 1/2 distance of two endpoints of confidence interval
```{r}
(round(x + zalpha2 * sigma/sqrt(n), 1)-round(x - zalpha2 * sigma/sqrt(n), 1)) /2
```
**(c). Obtain the margin of error by using the formula $E=z_{\frac{\alpha}{2}}.\frac{\sigma}{\sqrt{n}}$**

**Identify the critical value.**
```{r}
zalpha2
round(zalpha2,2)
```
We can find margin of error
```{r}
E = zalpha2 * sigma/sqrt(n)
E
round(E, 1)
```
<hr />
**Hope that helps!**