---
title: "10.3.77"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 10.3.77

Provided below are summary statistics for independent simple random samples from two populations. Use the nonpooled​ t-test and the nonpooled​ t-interval procedure to conduct the required hypothesis test and obtain the specified confidence interval.

$\bar x_{1} = 18, s_1=3, n_1=20$

$\bar x_{2} = 21, s_2=5, n_2=15$

<br/>

**(a).​ What are the correct hypotheses for a​ left-tailed test?**

Since it is a left-tailed test, the correct hypothese is 

$H_0: \mu_1 =\mu_2$

$H_a: \mu_1 < \mu_2$

**Find the test statistic. (Round to three decimal places as​ needed.)**

First, we need to get the data from the question
```{r}
x1 = 18
s1 = 3
n1 = 20
x2 = 21
s2 = 5
n2 = 15
```
<hr />
This is a nonpooled t-test, to compute the test statistic t we use the formular 
$t= \frac{\bar x_1-\bar x_2}{\sqrt{s_1^2/n_1+s_2^2/n_2}}$
```{r}
t=(x1-x2)/sqrt((s1^2/n1)+(s2^2)/n2)
t
```
Round the answer to three decimal places
```{r}
round(t,3)
```
**Now determine the critical values. (Round to three decimal places as​ needed.)**

We need to find degree of freedom by using the formula
$\Delta=\frac{[(s_1^2/n_1)+(s_2^2/n_2)]^2}{\frac{(s_1^2/n_1)^2}{n_1-1}+\frac{(s_2^2/n_2)^2}{n_2-1}}$
```{r}
deg = ((s1^2/n1) + (s2^2/n2))^2 / ( (s1^2/n1)^2/(n1-1) + (s2^2/n2)^2/(n2-1) )
```
Round down to nearest interger
```{r}
deg = floor(deg)
```
Since this is a left-tailed test and $\alpha = .05$, the area to the left of $\alpha$ is equal to $\alpha$
```{r}
alpha = .05
t_critical = abs(qt(alpha,deg))
t_critical
```
**Since we use abs() command so it return the positive value of $t_{\alpha}$**
Round the answer to three decimal places
```{r}
round(t_critical,3)
```
Since our test statistic t = -2.062 < our critical value $t_{\alpha}$ = -1.721, out test statistic lies in the rejected region. So we have enough evidence to reject null hypothesis.
<hr />
<br/>
**(b) The 90% confidence interval is from... to...​(Round to three decimal places as​ needed.)**

90% confidence interval means $\alpha = .1$ so our critical value $=\alpha/2=.05$ $t_{\alpha/2} = t_{critical value}$

To find confidence interval we use the formular $(\bar x_1 - \bar x_2) \pm t_{\alpha/2}.\sqrt{s_1^2/n_1+s_2^2/n_2}$

```{r}
(x1-x2) + t_critical * sqrt(s1^2/n1+s2^2/n2)
(x1-x2) - t_critical * sqrt(s1^2/n1+s2^2/n2)
```
Round to three decimal places
```{r}
round((x1-x2) + t_critical * sqrt(s1^2/n1+s2^2/n2),3)
round((x1-x2) - t_critical * sqrt(s1^2/n1+s2^2/n2),3)
```
We finish a lot of complicated work by using R
<hr />
**Hope that helps!**