---
title: "8.3.130"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 8.3.130

The following data represent the concentration of organic carbon​ (mg/L) collected from organic soil. Construct a 99% confidence interval for the mean concentration of dissolved organic carbon collected from organic soil.​ (Note: $\bar x$ = 16.56 mg/L and s = 8.3 mg/L)
<br/>

**Construct a 99​% confidence interval for the mean concentration of dissolved organic carbon collected from organic soil.**

Since the question gives t-distribution table we will use t-test.

First, we need to get the data from Excel. (The approach below gets the data mannually)
```{r}
data <- c(14.00,  8.81, 30.91, 19.80, 29.80,  7.40, 14.86, 14.86, 27.10, 20.46, 14.00,  8.09, 16.51, 14.90, 15.35,  5.30,  7.40, 33.67,  9.72, 18.30)
```
<hr />
To get 99% confidence interval, we run
```{r}
t.test(data, conf.level = .99)
```
<hr />
To get the data in 2 decimal places, we run 
```{r}
print(t.test(data, conf.level = .99), 4)
```
As you can see 99% confidence interval is from 11.25, 21.87
```{r}
round(pnorm((16-17.14)/1.88)-pnorm((15-17.14)/1.88), 4)
```
<hr />
<br/>
**(b) Find the percentage of the tarantulas that have a carapace length exceeding 18 mm.**

First, we need to find z-score for 18mm
```{r}
(18-17.14)/1.88
```
<hr />
We get each probability to the left by using pnorm() command or using the table
```{r}
pnorm((18-17.14)/1.88 )
```
<hr />
In order to get the data exceeding 18 mm
```{r}
1-pnorm((18-17.14)/1.88)
```
Round the answer two four decimal places
```{r}
round(1-pnorm((18-17.14)/1.88), 4)
```
<hr />
**(c) Determine and interpret the quartiles for the carapace length of these tarantulas.**

The area to the left of the first quartile is .25 

Using qnorm() to get the z-value
```{r}
qnorm(.25)
```

Using the formular x = mean + sigma * z-score
```{r}
17.14 + 1.88 * qnorm(.25)
round(17.14 + 1.88 * qnorm(.25), 2)
```

Since the area to the left of second and third quartile are .5 and .75 Using the same approach we have
```{r}
round(17.14 + 1.88 * qnorm(.5), 2)
round(17.14 + 1.88 * qnorm(.75), 2)
```
<hr />
**(d) Obtain the 95th percentile for the carapace length of these tarantulas**

The area to the left of 95th percentile is .95
```{r}
round(17.14 + 1.88 * qnorm(.95), 2)
```
<hr />
**Hope that helps!**