---
title: "13.4.75"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 13.4.75
The contingency table shown to the right gives a​ cross-classification of a random sample of values for two​ variables, x and​ y, of a population.

<br/>
<hr/>

**Find the test statistic.,$\chi^2$**

First we need to get the data from the question. (We can import it from Excel)
```{r}
data <- read.csv("~/R/Chapter 2/13.4.75/13.4.75.csv")
data
```
We store data into dframe
```{r}
dframe = data.frame(data)
dframe
```
<hr/>
Conditions to run a chi-square test

* All expected frequencies are 1 or greater

* At most 20% of the expected frequencies are less than 5

* The sample is a simple random sample

* The sample is an independent sample
<hr/>
**(a). Compute the expected frequencies and add them into the table given below.**

First we need to create a new data frame which does not contain a column of names so our data frame only contains data. 

We can use subset to drop column of name.
```{r}
dframe2 = subset(dframe, select = -c(X))
dframe2
```
To see the difference between dframe and dframe2, we can run
```{r}
dframe
```
**To find expected frequencies, we can run**
```{r}
chisq.test(dframe2, correct=FALSE)$expected
```
**b. The test statistic is **

We run chisq.test()
```{r}
chisq.test(dframe2, correct=FALSE)
round(chisq.test(dframe2, correct=FALSE)$statistic,2)
```
**(c). What are the null and alternative​ hypotheses?**
Since chi-square statistic test the independence of two variables, the correct hypothesis is

$H_0:$ The two variables, x and y, are not associated

$H_a:$ The two variables, x and y, are associated.

Since df = 1, to find critical value for $\alpha = .51$
```{r}
alpha = .05
round(qchisq(1- alpha,1),3)
```
Since $\chi^2$ is right-tailed test by nature, our test statistic lies in rejected region 30.86 > 3.841 , we have enough evidence to reject the hypothesis
<hr/>


<hr/>
**Hope that helps!**