---
title: "2.2.25"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 2.2.25

A list of college wrestling champions for the years 1981dash
2005 is given in the table. Each college has been associated with a particular letter. Use this data to complete parts (a) through (d).
<br/>

**(a) Determine a frequency distribution.**

First, we need to import the data from Excel.
(For simplicity, this imports mannual by hand, we can get the same result by importing dataset from Excel)
```{r}
data <- c("C", "B", "E", "B", "A", "B", "C", "A", "B", "C", "C", "B", "E", "C", "D", "B", "C", "A", "C", "A", "C", "B", "E", "A", "A")
data
```
<hr />
We can get the frequency by using table() command
```{r}
table(data)
```
<hr />
To display frenquency table in column format use cbind() command
```{r}
cbind(table(data))
```
<hr />
<br/>
**(b) Obtain a relative-frequency distribution.**

To display relative frenquency table in column format use cbind() command
```{r}
cbind(table(data)/length(data))
```
<hr />
To display the result appropriate to 5 decimal places use print() command

In this case, we have nice results so it does not show the difference.
```{r}
print(table(data)/length(data), 5)
```
<hr />
**(c) Draw a pie chart. Choose the correct chart below.**

Store relative-frequency table in a variable x 
```{r}
x <- table(data)/length(data)
```
Display pie chart using pie() command
```{r}
pie(x)
pie(x, labels = x)
```

<hr />
**(d) Construct a bar chart. Choose the correct chart below.**

Display bar chart using barplot() command
```{r}
barplot(x)
```
<hr/>
**Hope that helps!**