---
title: "12.1.31"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 12.1.31

For the specified margin of error and confidence​ level, obtain a sample size that will ensure a margin of error of at most the one specified.

margin of error = 0.05​; confidence level = 95%
<br/>
<hr/>
Since confidence level is .95, $\alpha = 1 - .95 = .05$. So $\alpha/2=.05/2$

We can find $z_{\alpha/2}$ by using qnorm()
```{r}
alpha = .05
zalpha2= abs(qnorm(alpha/2))
E = .05
```
From question 12.1.25 we can find the margin of error for a​ 95% confidence interval by using the formular $E=z_{\alpha/2}.\sqrt{\frac{\hat{p}(1-\hat{p})}{n}}$

This question is reverse, instead of finding E, the question gives us margin of error E and confidence level, ask us to find sample size n to meet the requirement. 

As professor Covert introduces in chapter 12 worksheet, we can derive the formula $E=z_{\alpha/2}.\sqrt{\frac{\hat{p}(1-\hat{p})}{n}}$ 

to $n=\hat{p}.(1-\hat{p}).(\frac{z_{\alpha/2}}{E})^2$

Since the proportion $\hat{p}$ runs from 0 to 1 so $\hat{p}.(1-\hat{p})$ will have the maximum value at $\hat{p}=.5$ or $\hat{p}.(1-\hat{p}) =.25$ 

For example, if we let $\hat{p} = x$ and $y= \hat{p}.(1-\hat{p})$ we have $y = -x^2 + x$. This parabola has vertex at $x=-\frac{b}{2a}=-\frac{1}{2.(-1)}=\frac{1}{2}$ and $y = -(\frac{1}{2})^2+\frac{1}{2}=\frac{1}{4}$

Since we do not know the sample proportion $\hat{p}$, we know that $n \le \frac{1}{4}.(\frac{z_{\alpha/2}}{E})^2$

The question asks obtain a sample size that will ensure a margin of error of **at most** the one specified.

We find the sample size by using the formula $n = \frac{1}{4}.(\frac{z_{\alpha/2}}{E})^2$

```{r}
n = 0.25 * (zalpha2 / E)^2
n
```
Round up to nearest integer
```{r}
ceiling(n)
```
<hr/>
**Hope that helps!**