---
title: "9.4.85"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 9.4.85

The recommended dietary allowance​ (RDA) of iron for adult females is 18
milligrams​ (mg) per day. The given iron intakes​ (mg) were obtained for 45
random adult females. At the 10​% significance​ level, do the data suggest that adult females​ are, on​ average, getting less than the RDA of 18
mg of​ iron? Assume that the population standard deviation is 4.6mg. Preliminary data analyses indicate that applying the​ z-test is reasonable.​ (Note: $\bar x$ =14.66 )

<br/>

**The test statistic is z = **

First, we need to import data from Excel. (Here we get the data mannually)
```{r}
data = c(14.9, 17.5, 14.7, 14.7, 10.6, 18.5, 18.1, 18.8, 15.4, 16, 12.6, 16.3, 21.1, 19.1, 11.6, 12.5, 15.1, 11, 15.3, 9.5, 18.8, 17.8, 13.9, 16.3, 11.6, 15.9, 12.6, 14.5, 11.4, 13, 18.5, 13, 11.7, 10.8, 17.7, 12, 17.7, 6.4, 16.9, 12.6, 16.5, 14.7, 13.2, 16.8, 12)
```
<hr />
The question provides sample mean $\bar x$ =14.66. Since we have the data, we could check it by running mean() command
```{r}
mean(data)
round(mean(data), 2)
```
**The given iron intakes​ (mg) were obtained for 45 random adult females.**
So the sample size is 45. We can get it by using length() command
```{r}
length(data)
```
**Assume that the population standard deviation is 4.6 mg.**

Since the question assumes that we know the population standard deviation and the sample size is greater 30. We can run z-test. 

If the population standard deviation is unknown and the sample size is small, t-test is prefered. 

**At the 10 ​% significance​ level, do the data suggest that adult females​ are, on​ average, getting less than the RDA of 18 mg of​ iron**
$H_0: \mu = 18 mg$
$H_a: \mu < 18 mg$

Now, we need to import the data from the question
```{r}
x = 14.66
mu = 18
n = 45
sigma = 4.6
```
To get the test statistic z we use the formular $z = (\bar x-\mu)/(\sigma/\sqrt{n})$, we run
```{r}
z = (x-mu)/(sigma/sqrt(n))
z
```
Round the answer to two decimal places
```{r}
round(z,2)
```
<hr />
<br/>
**Determine the critical​ value(s). Select the correct choice below and fill in the answer box within your choice.​(Round to two decimal places as​ needed.).**

First, this is a left tail test since $H_a: \mu < 18$, we have the negative critical value which is on the left of the graph.

Since the significance level is 10%, we can use qnorm() to get the z value
```{r}
qnorm(.1)
```
<hr />
Round to two decimal places
```{r}
round(qnorm(.1), 2)
```
<hr />
Since our test statistic z = -4.87 < our critical value $z_{\alpha}$ = -1.28, out test statistic lies in the rejected region. So we have enough evidence to reject null hypothesis.

<hr />
**Hope that helps!**