---
title: "10.2.41"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 10.2.41

Provided below are summary statistics for independent simple random samples from two populations. Use the pooled​ t-test and the pooled​ t-interval procedure to conduct the required hypothesis test and obtain the specified confidence interval.

$\bar x_{1} = 19, s_1=3, n_1=10$

$\bar x_{2} = 17, s_2=4, n_2=15$

<br/>

**(a).First, what are the correct hypotheses for a right-tailed test?**

Since it is a right-tailed test, the correct hypothese is 

$H_0: \mu_1 =\mu_2$

$H_a: \mu_1 > \mu_2$

**Next, compute the test statistic. (Round to three decimal places as​ needed.)**

First, we need to get the data from the question
```{r}
x1 = 19
s1 = 3
n1 = 10
x2 = 17
s2 = 4
n2 = 15
```
<hr />
This is a pooled t-test, to compute pooled sample standard deviation we use the formula 
$s_p= \frac{(n_1-1)s_1^2+(n_2-1)s_2^2}{n_1+n_2-2}$
```{r}
sp = sqrt( ( (n1-1)*s1^2 + (n2-1)*s2^2 )/ (n1+n2-2) )
sp
```
To get the test statistic t we use the formular 
$t= \frac{\bar x_1-\bar x_2}{s_p \sqrt{1/n_1+1/n_2}}$, we run
```{r}
t = (x1-x2)/(sp*sqrt(1/n1+1/n2))
t
```
Round the answer to three decimal places
```{r}
round(t,3)
```
**Now determine the critical values. (Round to three decimal places as​ needed.)**

We need to find degree of freedom
```{r}
deg = n1+n2-2
```
Since this is a right-tailed test and $\alpha = .01$, the area to the left of alpha is equal to $1-\alpha$
```{r}
alpha = .05
t_critical = abs(qt(1-alpha,deg))
t_critical
```
Round the answer to three decimal places
```{r}
round(t_critical,3)
```
Since our test statistic t = 1.345 < our critical value $t_{\alpha}$ = 1.714, out test statistic does not lie in the rejected region. So we do not have enough evidence to reject null hypothesis.
<hr />
<br/>
**(b) The 90% confidence interval is from... to...​(Round to three decimal places as​ needed.)**

90% confidence interval means $\alpha = .1$ so our critical value $=\alpha/2=.05$ $t_{\alpha/2} = t_{critical value}$

To find confidence interval we use the formular $(\bar x_1 - \bar x_2) \pm t_{\alpha/2}.s_p\sqrt{1/n_1+1/n_2}$

```{r}
(x1-x2) - t_critical*sp*sqrt(1/n1+1/n2)
(x1-x2) + t_critical*sp*sqrt(1/n1+1/n2)
```
Round to three decimal places
```{r}
round((x1-x2) - t_critical*sp*sqrt(1/n1+1/n2),3)
round((x1-x2) + t_critical*sp*sqrt(1/n1+1/n2),3)
```
We finish a lot of complicated work by using R
<hr />
**Hope that helps!**