---
title: "12.1.25"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 12.1.25

Given below are the number of successes and sample size for a simple random sample from a population.x = 7​, n = 40​, 90​% level

<br/>

**(a). Determine the sample proportion.**
```{r}
x = 7
n = 40
p = x/n
p
```
$\hat{p} = .175$

**(b). Decide whether using the​ one-proportion z-interval procedure is appropriate.**
There are two conditions for one-proportion z interval:

1) simple random sample

2) x and n-x are 5 are greater

The first condition is passed since the question specifies a simple random sample

To check the second condition we can run 
```{r}
x >= 5
n-x >= 5
```

**(c). If​ appropriate, use the​ one-proportion z-interval procedure to find the confidence interval at the specified confidence level.**

**The 90% confidence interval is from ... to ...**

Since confidence level is .9, $\alpha = 1 - .9 = .1$. So $\alpha/2=.1/2$

We can find $z_{\alpha/2}$ by using qnorm()
```{r}
alpha = .1
zalpha2= abs(qnorm(alpha/2))
```
We can find the margin of error for a​ 90% confidence interval by using the formular $E=z_{\alpha/2}.\sqrt{\frac{\hat{p}(1-\hat{p})}{n}}$
```{r}
E = zalpha2 * sqrt(p*(1-p)/n)
E
```
Round to three decimal places
```{r}
round(E, 3)
```

We can calculate 90% confidence interval by using the formula $\hat{p} \pm E$

or we can calculate it directly by using the formula 
$\hat{p} \pm z_{\alpha/2}.\sqrt{\frac{\hat{p}(1-\hat{p})}{n}}$ 

**These two formula gives the same answer**

```{r}
p + E
p - E
```
Round to three decimal places
```{r}
round(p + E, 3)
round(p - E, 3)
```

**Second approach: we use direct formula**
```{r}
p + zalpha2 * sqrt(p*(1-p)/n)
p - zalpha2 * sqrt(p*(1-p)/n)
```
Round to three decimal places
```{r}
round(p + zalpha2 * sqrt(p*(1-p)/n), 3)
round(p - zalpha2 * sqrt(p*(1-p)/n), 3)
```

**(d). If​ appropriate, find the margin of error for the estimate of p and express the confidence interval in terms of the sample proportion and the margin of error**

If we use the first approach, we already calculate the value of margin of error.
```{r}
round(E, 3)
```
If we use the second approach, we have to find the value of margin of error one more time. 

**The first approach is nicer and cleaner to use **
<hr/>
**Hope that helps!**