---
title: "12.2.81"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 12.2.81

The number of successes and the sample size for a simple random sample from a population are given below.
$x = 8, n = 32, H_0: p=0.2, H_a:p \ne 0.2, \alpha =.05$
b. Decide whether using the​ one-proportion z-test is appropriate.
c. If​ appropriate, use the​ one-proportion z-test to perform the specified hypothesis test.

<br/>

**(a). Determine the sample proportion.**
We use the formula $\hat{p}= \frac{x}{n}$
```{r}
x = 8
n = 32
p = x/n
p
```
$\hat{p} = .25$

**(b). Decide whether using the​ one-proportion z-interval procedure is appropriate.**
There are two conditions for one-proportion z test:

1) simple random sample

2) $np_0$ and $n(1-p_0)$ are 5 are greater

The first condition is passed since the question specifies a simple random sample

To check the second condition we can run 
```{r}
p0 = .2
n*p0 >=5
n*(1-p0) >=5
```

**(c).If​ appropriate, use the​ one-proportion z-test to perform the specified hypothesis test.**

To compute test statistic z we use the formula $z=\frac{\hat{p}-p_0}{\sqrt{p_0(1-p_0)/n}}$

```{r}
z = (p-p0)/sqrt(p0*(1-p0)/n)
z
```
Round to two decimal places
```{r}
round(z,2)
```

**Identify the critical​ value(s), if appropriate. Select the correct choice below​ and, if​ necessary, fill in the answer box to complete your answer.**

Since we have $H_a:p \ne .2$, this is a two tailed test with $\alpha = 0.05$. So $\alpha/2= .05/2$

To find negative critical value, we run
```{r}
round(qnorm(.05/2),2)
```
Since $-z_{\alpha/2}=-1.96< z = .71< z_{\alpha/2}=1.96$, the test statistic does not lie in rejected region. We do not have enough evidence to reject hypothesis.
<hr/>
**Hope that helps!**