---
title: "16.3.60"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 16.3.60

Researchers analyzed IQ data on preterm children at age​ 7-8 years. The mothers of the children in the study had chosen whether to provide their infants with breast milk within 72 hours of delivery. The researchers used the following designations. Group​ I: mothers declined to provide breast​ milk; Group​ IIa: mothers had chosen but were unable to provide breast​ milk; and Group​ IIb: mothers had chosen and were able to provide breast milk. The summary statistics on IQ are at the right. At the 1​% significance​ level, do the data provide sufficient evidence to conclude that a difference exists in mean IQ at age​ 7-8 years for preterm children among the three​ groups? Critical values are given at the right.
<br/>

<hr/>
Notation in one-way ANOVA:

  * k = number of populations
  
  *  n = total number of observations
  
  * $\bar x$ = mean of all n observations
  
  * $n_j$ = size of sample from Population j
  
  * $\bar{x_j}$ = mean of sample from Population j
  
  * $s_j^2$ = variance of sample from Population j
  
  * $T_j$ = sum of sample data from Population j
</hr>
Defining formulas from sums of squares in one-way ANOVA:

 * SST = $\sum (x_i - \bar x)^2$
  
 * SSTR = $\sum n_j(\bar{x_j} - \bar{x})^2$
  
 * SSE = $\sum (n_j-1)s_j^2$
  
<hr/>
One-way ANOVA identity: SST = SSTR + SSE
<hr/>
Computing formulas from sums of squares in one-way ANOVA:

 * SST = $\sum x_i^2 - (\sum x_i)^2/n$
  
 * SSTR = $\sum (T_j^2/n_j) - (\sum x_i)^2/n$
  
 * SSE = SST - SSTR
  
  **The way they define $\sum (T_j^2/n_j)$ is different from the one for x**
<hr/>
Mean squares in one-way ANOVA:

 * MSTR = $\frac{SSTR}{k-1}$
  
 * MSE = $\frac{SSE}{n-k}$
  
 * SSE = SST - SSTR
  
<hr/>
Test statistic for one-way ANOVAA (independent samples, normal populations, and equal population standard deviations):

 * F = $\frac{MSTR}{MSE}$
  
with df = (k - 1, n - k)
  
<hr/>

Confidence interval for $\mu_i - \mu_j$ in the Tukey multiple-comparison method (independent samples, normal populations, and equal population sstandard deviations):

 * $(\bar{x_i} - \bar{x_j}) \pm \frac{q_{\alpha}}{\sqrt{2}}.s\sqrt{\frac{1}{n_i} + \frac{1}{n_j}}$

where s = $\sqrt{MSE}$ and $q_{\alpha}$ is obtained for a q-curve with parameters k and n - k
  
<hr/>
Test statistic for a Kruskal-Wallis test (independent samples, same-shape populations, all sample sizes 5 or greater):

  * $K=\frac{SSTR}{SST/(n-1)}$ or
  
  * $K=\frac{12}{n(n+1)}\sum_{j=1}^{k} \frac{R_j^2}{n_j} - 3(n+1)$
  

where SSTR and SST are computed for the ranks of the data, and $R_j$ denotes the sum of the ranks for the sample data from Population j. K has approximately a chi-square distribution with df = k -1
  
<hr/>

<hr/>
**(a) Find the null and alternative hypotheses. Choose the correct answer below.**

Since the question asks that "a difference exists in mean IQ at age​ 7-8 years for preterm children among the three​ groups", the correct hypothesis is.

$H_0: \mu_I = \mu_{IIa} = \mu_{IIb}$

$H_a:$ Not all the means are equal.

First we need to get the data from the question. 
```{r}
nj <- c(88, 17, 195)
x <- c(98.6, 97.3, 101.3)
s <- c(11.5, 20.6, 13.1)
```


**Names of variables**


n = total number of observations: n

<hr/>

We find SSTR, SSE, SST by using defining formula 
 
```{r}
n = sum(nj)
k = length(x)
```
**Find SSTR using the formula SSTR = $\sum n_j(\bar{x_j} - \bar{x})^2$**
```{r}
SSTR = sum(nj*(x- sum(nj*x)/sum(nj))^2)
SSTR
round(SSTR, 2)
```
**Find SSE using the formula SSE = $\sum (n_j-1)s_j^2$**
```{r}
SSE = sum((nj-1)*s^2)
SSE
round(SSE, 2)
```
**Find SST, we use formula SST = SSE + SSTR **

```{r}
SST = SSE + SSTR
SST
round(SST, 2)
```

<hr/>
**Find df treatment **
```{r}
k = length(x)
k-1
```
**Find SS treatment **
```{r}
SSTR
```
**Find MS treatment **
```{r}
MSTR = SSTR/(k-1)
MSTR
```
**Find Error df **
```{r}
n - k
```
**Find Error SS **
```{r}
SSE
```
**Find Error MS **
```{r}
MSE = SSE / (n - k)
MSE
```
**Find F-statistic treatment **
```{r}
MSTR / MSE
round(MSTR / MSE, 2)
```
**Find df total**
```{r}
n - 1
```
**Find SS total**
```{r}
SST
```
<hr/>

**Find the critical value.**

Since $\alpha = .01$
```{r}
alpha = 0.01
qf(1-alpha, k-1, n-k)
```
Round to decimal places
```{r}
round(qf(1-alpha, k-1, n-k), 2)
```

Since our test statistic = 1.73 < our critical value $F_{\alpha}$=4.68 and it is a right-tailed test, we do not have enough evidence to reject the hypothesis.
<hr/>
**Hope that helps!**