---
title: "9.4.77"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 9.4.77

A sample​ mean, sample​ size, and population standard deviation are provided below. Use the​ one-mean z-test to perform the required hypothesis test at the 1%  significance level.

$\bar x$ = 17, n =34, $\sigma$ = 10, $H_0: \mu =22, H_a: \mu < 22$
<br/>

**The test statistic is z = **

First, we need to get the data the question
```{r}
x = 17
n = 34
sigma = 10
mu = 22
```
<hr />
To get the test statistic z we use the formular $z = (\bar x-\mu)/(\sigma/\sqrt{n})$, we run
```{r}
z = (x-mu)/(sigma/sqrt(n))
z
```
Round the answer to two decimal places
```{r}
round(z,2)
```
<hr />
<br/>
**(b) Identify the critical​ value(s). Select the correct choice below and fill in the answer box within your choice.​(Round to two decimal places as​ needed.).**

First, this is a left tail test since $H_a: \mu < 22$, we have the negative critical value which is on the left of the graph.

Since the significance level is 1%, we can use qnorm() to get the z value
```{r}
qnorm(.01)
```
<hr />
Round to two decimal places
```{r}
round(qnorm(.01), 2)
```
<hr />
Since our test statistic z = -2.92 < our critical value $z_{\alpha}$ = -2.33, out test statistic lies in the rejected region. So we have enough evidence to reject null hypothesis.

<hr />
**Hope that helps!**