---
title: "10.5.161"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 10.5.161

A group of 8 students were given the same standardized test twice to see whether retaking the test affected the score. The table gives the score differences for the 8students. Use the paired​ t-interval procedure to determine a 95%  confidence interval for the difference between the mean scores on the first test and the second test​ (retake). 
(Note: $\bar d = -1.25, s_d = 50.55$)

<br/>

**The 95% confidence interval is from ... to ...**

First, we need to get the data from the question. (We could import the data from Excel)
```{r}
difference <- c(-30, 30, -40, -40, 80, 60, -50, -20)
```
We can check the data from Note
```{r}
round(mean(difference),2)
round(sd(difference),2)
```
<hr />
We have confidence level = .95

**First approach use t.test()**
```{r}
t.test(difference, conf.level = .95)
```
Round to 2 decimal places
```{r}
print(t.test(difference, conf.level = .95),4)
```

**Second appraach to find confidence interval, we can use formula**
$\bar d \pm t_{\alpha/2}.\frac{s_d}{\sqrt{n}}$

Since the confidence level = .95, we have $\alpha = .05$
```{r}
alpha = .05
n = length(difference)
talpha2 = abs(qt(alpha/2, n-1))
mean(difference) + talpha2 *(sd(difference)/sqrt(n))
mean(difference) - talpha2 *(sd(difference)/sqrt(n))
```
Round to 2 decimal places
```{r}
round(mean(difference) + talpha2 *(sd(difference)/sqrt(n)),2)
round(mean(difference) - talpha2 *(sd(difference)/sqrt(n)),2)
```
**It is good to know both approaches so we could check the answer from t.test() in R**
<hr/>
**Hope that helps!**