---
title: "13.2.18"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 13.2.18

A distribution and the observed frequencies of the values of a variable from a simple random sample of the population are provided below. Use the​ chi-square goodness-of-fit test to​ decide, at the specified significance​ level, whether the distribution of the variable differs from the given distribution.

Distribution: 0.1875, 0.1875, 0.3125, 0.3125
Observed frequencies: 20, 22, 20, 34
Significance level = 0.05
<br/>
<hr/>
**Determine the null and alternative hypotheses. Choose the correct answer below.**

Since the question asks whether the distribution of the variable differs from the given distribution, it is a two-tailed test

$H_0:$ The distribution of the variable is the same as the given distribution

$H_a:$ The distribution of the variable differs from given distribution

**Compute the value of the test​ statistic,$\chi^2$**

First we need to get the data from the question. (We can import it from Excel)
```{r}
distribution <- c(0.1875, 0.1875, 0.3125, 0.3125)
obFrequency <- c(20, 22, 20, 34)
```

**First approach, we can use chisq.test()**
```{r}
chisq.test(obFrequency,p=distribution, correct=FALSE)
```
Round to 3 decimal places
```{r}
print(chisq.test(obFrequency,p=distribution, correct=FALSE),6)
```
<hr/>
**Second approach using formular**

We can find the test statistic $\chi^2$ by using the formula 
$\chi^2=\sum{\frac{(O-E)^2}{E}}$

Expected frequency = sample size * distribution

We can find the sample size by using sum(obFrequency) in R
```{r}
expFrequency = sum(obFrequency)*distribution
sum((obFrequency-expFrequency)^2/expFrequency)
```
Round to three decimal places
```{r}
round(sum((obFrequency-expFrequency)^2/expFrequency),3)
```
**$\chi^2$ is right-tailed test by nature**

Since we have $\alpha=.05$ and there are 4 possible values for the variable, so the degree of freedom df = 4 -1 = 3

$\chi_\alpha^2$ has $\alpha$ is the area to the right under $\chi$ curve 

We can get $\chi^2$ value by using the table or we can run qchisq()

qchisq() takes in the area to the left and degree of freedom

```{r}
alpha = .05
df =  4 - 1
qchisq(1-alpha,df)
```
Round to three decimal places
```{r}
round(qchisq(1- alpha,df),3)
```

**Since $\chi^2$ is right-tailed test by nature, our test statistic does not lie in rejected region 4.978 < 7.815 , we do not have enough evidence to reject the hypothesis**
<hr/>
**Hope that helps!**