---
title: "2.3.65"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 2.3.65

A simple quantitative data set has been provided. Use limit grouping with a first class of 0-4and a class width of 5 to complete parts (a) through (d) for this data set.
<br/>

**(a) Determine a frequency distribution.**

First, we need to import the data from Excel.
(For simplicity, this imports mannual by hand, we can get the same result by importing dataset from Excel)
```{r}
data <- c(21, 6, 2, 4, 2, 23, 17, 9, 24, 12, 3, 22, 26, 28, 9, 18, 4, 27, 0, 26)
data
```
<hr />
We can get the frequency by using table() command
```{r}
table(data)
```
<hr />
To display bin frenquency table use as.data.frame() command
```{r}
k = as.data.frame(table(cut(data, breaks=seq(0,30, by=5))))
k
```
<hr />
Since R does not count the value 0, we could double check the value in range 0-4 and readjust the value 
```{r}
f = k$Freq
f
f[1] = 6
f
```
<hr />
<br/>
**(b) Obtain a relative-frequency distribution.**

To display relative frenquency table in column format use cbind() command
```{r}
f/length(data)
```
<hr />
To display the result appropriate to 5 decimal places use print() command

In this case, we have nice results so it does not show the difference.
```{r}
print(f/length(data), digits = 5)
```

<hr />
**(c) Construct a frequency histogram based on your result from part (a). Choose the correct histogram below.**

Display bar chart using barplot() command
```{r}
barplot(f)
```
<hr/>
**(d) Construct a relative-frequency histogram based on your result from part (b). Choose the correct histogram below.**

The relative-frequency histogram should have the same behavior with the one in part (c). We can get histogram plot by using barplot() command
```{r}
barplot(f/length(data))
```
<hr />
**Hope that helps!**