---
title: "8.1.11"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 8.1.11

For the provided sample​ mean, sample​ size, and population standard​ deviation, complete parts​ (a) through​ (c) below

$\bar{x}=37, n=64, \sigma=3$
<br/>

**(a). Find a​ 95% confidence interval for the population mean.**


First, we need to get the data from the question
```{r}
x = 37
n = 64
sigma = 3
```
<hr />
Empirical rule:

* 99.7% - 1 standard deviation

* 95% - 2 standard deviation

* 68% - 3 standard deviation
<hr/>


To find 95% confidence interval, we run
```{r}
x - 2 * sigma/sqrt(n)
x + 2 * sigma/sqrt(n)
```
Round to two decimal places as needed
```{r}
round(x - 2 * sigma/sqrt(n), 2)
round(x + 2 * sigma/sqrt(n), 2)
```
**(b). Identify and interpret the margin of error.**

Margin of error = 1/2 distance of two endpoints of confidence interval
```{r}

(round(x + 2 * sigma/sqrt(n), 2) - round(x - 2 * sigma/sqrt(n), 2)) /2
```
**(c). Express the endpoints of the confidence interval in terms of the point estimate and the margin of error.**

We can find margin of error
```{r}
round( 2 * sigma/sqrt(n), 2)
```
<hr />
**Hope that helps!**