---
title: "7.1.13"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 7.1.13

The data in the table represent the ages of the winners of an award for the past five years. Use the data to answer questions​ (a) through​ (e).
​(Assume that sampling is without​ replacement.)
<br/>

**(a)Find the population mean age of the five winners.**

First, we need to import the data from Excel. Illustrations shows importing data mannually
```{r}
data <- c(37,42,49,49,43)
```
<hr />
We use mean() command to find the population mean
```{r}
mean(data)
```
<hr />
<br/>
**(b) For samples of size​ 3, construct a table of all possible samples and their sample means.**

To construct the table of all possible samples of size 3, we use combn() command
```{r}
combn(data,3)
```
<hr />
To find sample mean, we run
```{r}
x = combn(data, 3, mean)
x
```
<hr />
Round the answer to 2 decimal places
```{r}
print(x, 4)
```
<hr />
**(c) Draw a dotplot for the sampling distribution of the sample mean for samples of size 3. Choose the correct dotplot below.**

To draw a dotplot for sample mean, we use stripchart() command. method="stack" shows the data on top of each other. pch=20 represents dark circle as a data. cex=3 indicates the size of circle. 
```{r}
stripchart(x, method="stack", pch=20, cex =3)
```

R provides dotchart() command which gives a chart slightly different from the one in Pearson.
You could try it by running dotchart()
```{r}
dotchart(as.numeric(x))
```

<hr />
**(d) For a random sample of size​ 3, what is the chance that the sample mean will equal the population​ mean?**

Firstly, we need to round sample means to 2 decimal places
```{r}
x = round(x,2)
x
```
We can use table() command to get the frequency table
```{r}
table(x)
```
We can check mannually z.if the mean is in the frequency table or we can run 
```{r}
table(x)[names(table(x)) == 44]
```
Since the frequency is 0, the chance is 0 
<hr />

**(e) For a random sample of size​ 3, obtain the probability that the sampling error made in estimating the population mean by the sample mean will be 3 years or​ less; that​ is, determine the probability that x overbar will be within 3 years of mu.**

To find the lower and upper bound, we run 
```{r}
44 - 3
44 + 3
```
We can use table() command to get the frequency table
```{r}
table(x)
```
Since the frequency between these range is 9, we can find the probability by running 
```{r}
9/length(x)
```
<hr />
**Hope that helps!**