---
title: "6.3.97"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 6.3.97

According to a recent study, the carapace length for adult males of a certain species of tarantula are normally distributed with a mean of $\mu$ = 17.14
mm and a standard deviation of $\sigma$ = 1.88
mm. Complete parts​ (a) through​ (d) below.
<br/>

**(a)Find the percentage of the tarantulas that have a carapace length between 15 mm and 16 mm.**

First, we need to find z-score for 15mm and 16mm by using the formula $z=\frac{x-\mu}{\sigma}$
```{r}
(15-17.14)/1.88
(16-17.14)/1.88 
```
<hr />
We get each probability to the left by using pnorm() command or using the table
```{r}
pnorm((16-17.14)/1.88 )
pnorm((15-17.14)/1.88 )
```
<hr />
In order to get the data between the range 15 and 16 we subtract these probabilities above
```{r}
pnorm((16-17.14)/1.88)-pnorm((15-17.14)/1.88)
```
Round the answer two four decimal places
```{r}
round(pnorm((16-17.14)/1.88)-pnorm((15-17.14)/1.88), 4)
```
<hr />
<br/>
**(b) Find the percentage of the tarantulas that have a carapace length exceeding 18 mm.**

First, we need to find z-score for 18mm
```{r}
(18-17.14)/1.88
```
<hr />
We get each probability to the left by using pnorm() command or using the table
```{r}
pnorm((18-17.14)/1.88 )
```
<hr />
In order to get the data exceeding 18 mm
```{r}
1-pnorm((18-17.14)/1.88)
```
Round the answer two four decimal places
```{r}
round(1-pnorm((18-17.14)/1.88), 4)
```
<hr />
**(c) Determine and interpret the quartiles for the carapace length of these tarantulas.**

The area to the left of the first quartile is .25 

Using qnorm() to get the z-value
```{r}
qnorm(.25)
```

Using the formula $x = \mu + \sigma . z$
```{r}
17.14 + 1.88 * qnorm(.25)
round(17.14 + 1.88 * qnorm(.25), 2)
```

Since the area to the left of second and third quartile are .5 and .75 Using the same approach we have
```{r}
round(17.14 + 1.88 * qnorm(.5), 2)
round(17.14 + 1.88 * qnorm(.75), 2)
```
<hr />
**(d) Obtain the 95th percentile for the carapace length of these tarantulas**

The area to the left of 95th percentile is .95
```{r}
round(17.14 + 1.88 * qnorm(.95), 2)
```
<hr />
**Hope that helps!**