---
title: "3.1.19"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 3.1.19

A concrete mix is designed to withstand 3000 pounds per square inch​ (psi) of pressure. The following data represent the strength of nine randomly selected casts​ (in psi). Compute the​ mean, median and mode strength of the concrete​ (in psi).
<br/>
<hr/>
**Recommended find manually in Excel **
<hr/>
* even number of data set - type 5
* odd number of data set - type 1
<hr/>

First, we need to import the data from Excel.
(For simplicity, this imports manually by hand, we can get the same result by importing dataset from Excel)
```{r}
x <- c(3970, 4080, 3100, 3200, 2930, 3830, 4080, 4040, 3530)
x
```
<hr />
We can sort the data
```{r}
sort(x)
```
**Compute the mean strength of the concrete.**

```{r}
mean(x)
```
<hr />
**Compute the median strength of the concrete.**

```{r}
median(x)
```

```{r}
length(x)
```
Since we have odd amount of data
```{r}
summary(x, quantile.type = 1)
```
**Compute the mode strength of the concrete.**

```{r}
table(x)
```
<hr/>
**Hope that helps!**