---
title: "12.1.17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 12.1.17

A poll found that 59% of a random sample of 1058 adults said that they believe in ghosts.

<br/>

**(a). Determine the margin of error for a​ 99% confidence interval. (Round to three decimal places as​ needed.)**

First, we need to get the data from the question. $\hat{p} = .59$
```{r}
n = 1058
p = .56
```

Since confidence level is .99, $\alpha = 1 - .99 = .01$. So $\alpha/2=.01/2$

We can find $z_{\alpha/2}$ by using qnorm()
```{r}
alpha = .01
zalpha2= abs(qnorm(alpha/2))
```
We can find the margin of error for a​ 99% confidence interval by using the formular $E=z_{\alpha/2}.\sqrt{\frac{\hat{p}(1-\hat{p})}{n}}$
```{r}
E = zalpha2 * sqrt(p*(1-p)/n)
E
```
Round to three decimal places
```{r}
round(E, 3)
```
<hr />

**(b). Without doing any​ calculations, indicate whether the margin of error is larger or smaller for a​ 90% confidence interval.**

If we change the confidence level from 99% to 90%, our $z_{\alpha/2}$ will become smaller since alpha increases. From the formular, we can see that margin of error E will decrease.
<hr/>
**Hope that helps!**