---
title: "3.4.171"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 3.3.171

An article by a researcher reported on a​ long-term study of the effects of hurricanes on tropical streams in forests. The study shows that one particular hurricane had a significant impact on stream water chemistry. The following table shows a sample of 10 ammonia fluxes in the first year after the hurricane. Data are in kilograms per hectare per year. Complete parts​ (a) through​ (e) below.
<br/>
<hr/>
**Recommanded find quatiles mannually in Excel since there is inconsistent approach in R **
<hr/>
* even number of data set - type 5
* odd number of data set - type 1
<hr/>

First, we need to import the data from Excel.
(For simplicity, this imports mannual by hand, we can get the same result by importing dataset from Excel)
```{r}
x <- c(88, 171, 64, 159, 89, 84, 180, 126, 123, 91)
x
```
<hr />
**(a). Obtain and interpret the quartiles**

Since we have even number of 
```{r}
summary(x, quantile.type=5)
quantile(x, type=5)
```
<hr />
**(b).Determine and interpret the interquartile range​ (IQR).**
We use the formula $IQR = Q_3-Q_1 $
```{r}
159-88
```
**(c). Find and interpret the​ five-number summary.**

We can see the summary from part (a)

To interpret five-number summary, we plot boxplot of data
```{r}
boxplot(quantile(x, type=5))
```

**(d). Identify potential​ outliers, if any. Choose the correct answer below​ and, if​ necessary, fill in the answer box to complete your choice**
<hr/>
* Lower limit = $Q_1 - 1.5.IQR$
* Upper limit = $Q_3 + 1.5.IQR$
<hr/>
Lower limit
```{r}
88 - 1.5 * 71
```
Upper limit
```{r}
159 + 1.5 * 71
```
Sort our data
```{r}
sort(x)
```
**Hope that helps!**