---
title: "9.5.111"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 9.5.111

A sample​ mean, sample​ size, and sample standard deviation are provided below. Use the​ one-mean t-test to perform the required hypothesis test at the 1​% significance level.


$\bar x$ = 21, s = 10, n = 32, $ $H_0: \mu =27, H_a: \mu \neq 27$
<br/>

**The test statistic is t = **

First, we need to get the data the question
```{r}
x = 21
s = 10
n = 32
mu = 27
```
<hr />
To get the test statistic t we use the formular $t = \frac{\bar x-\mu}{\frac{s}{\sqrt{n}}}$, we run
```{r}
t = (x-mu)/(s/sqrt(n))
t
```
Round the answer to two decimal places
```{r}
round(t,2)
```
<hr />
<br/>
**Identify the critical​ value(s). Select the correct choice below and fill in the answer box within your choice.(Round to three decimal places as​ needed.).**

First, this is a two tailed test since $H_a: \mu \neq 27$, we have two critical values.

We need to find degree of freedom
```{r}
deg = n-1
```

Since the significance level is 1% and this is a two tail test, the area to the left of a negative critical will be .01/2

We can find the negative critical value by use qt() command
```{r}
qt(.01/2, deg)
```
<hr />
Round to three decimal places
```{r}
round(qt(.01/2, deg),3)
```
<hr />
Since our test statistic t = -3.39 < our critical value $t_{\alpha/2}$ = -2.744, out test statistic lies in the rejected region. So we have enough evidence to reject null hypothesis.

<hr />
**Hope that helps!**