---
title: "5.2.31"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 5.2.31

The random variable X is the crew size of a randomly selected shuttle mission. Its probability distribution is shown below. Complete parts a through c.
<br/>
<hr/>
```{r}
data <- read.csv("~/R/Chapter 2/5.2.31  probability distribution/5.2.31.csv")
data
```
We store data into two variables x and P 
```{r}
x = data$x
x
P = data$P.X.x.
P
```
<hr/>
**(a). Find and interpret the mean of the random variable. **
```{r}
mu = sum(x*P)
mu
```
Round to three decimal places
```{r}
round(mu, 3)
```

**(b). Obtain the standard deviation of the random variable. **

We can find standard deviation by using formula $\sigma=\sqrt{\sum(x-\mu)^2P(X=x)}$
```{r}
sigma = sqrt(sum((x-mu)^2*P))
sigma
```
Round to three decimal places
```{r}
round(sigma, 3)
```
<hr/>
We can use alternative formula to find standarad deviation $\sigma=\sqrt{\sum x^2P(X=x)- \mu^2}$

```{r}
sigma2 = sqrt(sum(x^2*P)-mu^2)
sigma2
```

**(c). Draw a probability histogram for the random variable. Choose the correct graph below. **

```{r}
barplot(P, names.arg = x)
```

<hr/>
**Hope that helps!**