---
title: "12.3.101"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 12.3.101

The numbers of successes and the sample sizes for independent simple random samples from two populations are provided for a​ left-tailed test and an​ 80% confidence interval. Complete parts​ (a) through​ (d).
$x_1 = 20, n_1 = 50,x_2 = 23, n_2 = 50, \alpha =.10$

<br/>

**(a). Determine the sample proportion.**
We use the formula $\hat{p}= \frac{x}{n}$
```{r}
x1 = 20
n1 = 50
p1 = x1/n1
p1
```
$\hat{p_1} = .4$
```{r}
x2 = 23
n2 = 50
p2 = x2/n2
p2
round(p2,3)
```
$\hat{p_2} = .46$
```{r}
p = (x1 + x2)/(n1+n2)
p
round(p,3)
```
$\hat{p} = .43$

**(b) Decide whether using the​ two-proportions z-procedures is appropriate.**

There are two conditions for two-proportions z test:

1) simple random sample

2) $x_1,n_1-x_1,x_2,n_2-x_2,$ are 5 are greater

The first condition is passed since the question specifies a simple random sample

To check the second condition we can run 
```{r}
x1 >= 5
n1 - x1 >= 5
x2 >= 5
n2 - x2 >= 5
```

**(c).If​ appropriate, use the​ two-proportions z-test to conduct the required hypothesis test.What are the hypotheses for this​ test?.**
Since this is a left-tailted test, we have 

$H_0:p_1=p_2, H_a:p_1<p_2$

To compute test statistic z we use the formula $z=\frac{\hat{p_1}-\hat{p_2}}{\sqrt{\hat{p_p}(1-\hat{p_p})}.\sqrt{(\frac{1}{n_1})+(\frac{1}{n_2})}}$

```{r}
z  = (p1 -p2)/(sqrt(p*(1-p)) * sqrt(1/n1+1/n2))
z
```
Round to two decimal places
```{r}
round(z,2)
```

**Identify the critical​ value(s), if appropriate. Select the correct choice below​ and, if​ necessary, fill in the answer box to complete your answer.**

It is a left-tailed test with $\alpha = .1$, so the area to the left of critical value = .1

To find negative critical value, we run
```{r}
round(qnorm(.1),2)
```
Since $-z_{\alpha}=-1.28< z = -.61$ the test statistic does not lie in rejected region. We do not have enough evidence to reject hypothesis.

**(d) If​ appropriate, use the​ two-proportions z-interval procedure to find the specified confidence interval. Select the correct choice below​ and, if​ necessary, fill in the answer boxes to complete your answer.**

**The 80% confidence interval is from... to...**

**First approach we calculate confidence interval using margin of error **

To calculate margin of error we use formula $E=z_{\alpha/2}.\sqrt{\frac{\hat{p_1}(1-\hat{p1})}{n_1}+\frac{\hat{p_2}(1-\hat{p2})}{n_2}}$

Since the confidence level is .8, we have $\alpha = .2$ and $\alpha/2=.1$
```{r}
alpha = .2
zalpha2 = abs(qnorm(alpha/2))
E = zalpha2 * sqrt(p1*(1-p1)/n1 + p2*(1-p2)/n2)
E
```
To calculate the confidence interval, we use the formula
$(\hat{p_1}-\hat{p_2}) \pm E$
```{r}
(p1-p2) + E
(p1-p2) - E
```
Round to three decimal places
```{r}
round((p1-p2) + E, 3)
round((p1-p2) - E, 3)
```

**Second approach: find confidence interval directly without using margin of error E **

To calculate the confidence interval, we use the formula
$(\hat{p_1}-\hat{p_2}) \pm z_{\alpha/2}.\sqrt{\frac{\hat{p_1}(1-\hat{p_1})}{n_1}+\frac{\hat{p_2}(1-\hat{p_2})}{n_2}}$
```{r}
alpha = .2
zalpha2 = abs(qnorm(alpha/2))
(p1-p2) + zalpha2 * sqrt(p1*(1-p1)/n1 + p2*(1-p2)/n2)
(p1-p2) - zalpha2 * sqrt(p1*(1-p1)/n1 + p2*(1-p2)/n2)
```
Round to three decimal places
```{r}
round((p1-p2) + zalpha2 * sqrt(p1*(1-p1)/n1 + p2*(1-p2)/n2),3)
round((p1-p2) - zalpha2 * sqrt(p1*(1-p1)/n1 + p2*(1-p2)/n2),3)
```
<hr/>
**Notes: confidence interval is a range of data that contain unknown population and critical value is where we split the data to rejected and non-rejected region**
<hr/>
**Hope that helps!**