---
title: "14.3.100"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 14.3.100

Following are chest size and weight data for 8 randomly selected bears.​ Here, x denotes chest​ size, in​ inches, and y denotes​ weight, in pounds. Use the information to do parts​ (a) through​ (d).

$\sum x = 396, \sum y = 2362, \sum xy = 118330, \sum x^2 = 19870$
<br/>
<hr/>
**Compute​ SST, SSR, and​ SSE, using the​ formulas, .**

First we need to get the data from the question. (We can import it from Excel)
```{r}
x<- c(55, 44, 46, 58, 40, 54, 52, 47)
y<- c(325, 253, 263, 340, 251, 315, 310, 305)
```
<hr/>
From formula sheet

$S_{xx}=\sum(x_i-\bar{x})^2=\sum x_i^2-(\sum x_i)^2/n$

$S_{xy}=\sum(x_i-\bar{x})(y_i-\bar{y})=\sum x_iy_i-(\sum x_i)(\sum y_i)/n$

$S_{yy}=\sum(y_i-\bar{y})^2=\sum y_i^2-(\sum y_i)^2/n$

<hr/> Total sum of squares: 
$SST =\sum(y_i-\bar{y})^2 = S_{yy}$

Regression sum of squares: 
$SSR=\sum(\hat{y_i}-\bar{y})^2=S_{xy}^2/S_{xx}$

Error sum of squares:
$SSE=\sum (y_i-\hat{y_i})^2=S_{yy} - S_{xy}^2/S_{xx}$

Regression identity: 
$SST = SSR + SSE$

Coefficient of determination: 
$r^2=\frac{SSR}{SST}$

Linear correlation coefficient: 
$r=\frac{\frac{1}{n-1}\sum(x_i-\bar{x})(y_i-\bar{y})}{s_xs_y}$ or 
$r=\frac{S_{xy}}{\sqrt{S_{xx}S_{yy}}}$
<hr/>
**Names of variables**

$S_{xx}: Sxx$

$S_{xy}: Sxy$

$S_{yy}: Syy$


**First approach, we find SST, SSR, SSE without finding $\bar x, \bar y$**

```{r}
n = length(x)
```
We have the same dataset from the question.

Find $S_{xy}, S_{xx}, S_{yy}$
```{r}
Syy = sum(y*y) - sum(y)^2/n
Sxx = sum(x*x) - sum(x)^2/n
Sxy = sum(x*y) - sum(x) * sum(y) /n
```

```{r}
Sxx
Sxy
Syy
```
**Find SST**
```{r}
SST = Syy
SST
```
Round to two decimal places
```{r}
round(SST,2)
```

**Find SSR**
```{r}
SSR = Sxy^2/Sxx
SSR
```
Round to two decimal places
```{r}
round(SSR,2)
```
**Find SSE**
```{r}
SSE = Syy - Sxy^2/Sxx
SSE
```
Round to two decimal places
```{r}
round(SSE,2)
```
Check if SSE + SSR = SST
```{r}
SSE + SSR == SST
```
<hr/>
**Second approach finding SST, SSR, SSE using $\bar x, \bar y$ **

```{r}
Sxx = sum((x-mean(x))^2)
Sxy = sum((x-mean(x))*(y-mean(y)))
Syy = sum((y-mean(y))^2)
```

```{r}
Sxx
Sxy
Syy
```
<hr/>
**(b) Compute the coefficient of​ determination, $r^2$**

**First approach: using the formula**

Linear correlation coefficient
```{r}
r = Sxy/sqrt(Sxx*Syy)
r
```
Coefficient of​ determination $r^2$
```{r}
r^2
```
Round to four decimal places
```{r}
round(r^2, 4)
```
<hr/>
**Second approach: using summary() in R**

Multiple R-squared = coefficient of determination
```{r}
summary(lm(y~x))
```

**Third approach: using cor() in R**
To find r, we run
```{r}
cor(x,y)
```
To find $r^2$, we run
```{r}
cor(x,y)^2
```
Round to 4 decimal places
```{r}
round(cor(x,y)^2, 4)
```
<hr/>
**(c) Determine the percentage of variation in the observed values of the response variable explained by the​ regression, and interpret your answer.**

Show percentage value of $r^2$
```{r}
round(cor(x,y)^2, 4) * 100
```
<hr/>
**(d) State how useful the regression equation appears to be for making predictions. Choose the correct answer below.**

Since the $r^2$ value is close to 1, it is very useful to use regression equation
<hr/>
**Hope that helps!**