---
title: "10.2.51"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 10.2.51

Preliminary data analyses indicate that you can reasonably consider the assumptions for using pooled​ t-procedures satisfied. Independent random samples of released prisoners in the fraud and firearms offense categories yielded the following information on time​ served, in months. Obtain a 95 %
confidence interval for the difference between the mean times served by prisoners in the fraud and firearms offense categories.
(Note: $\bar x_1=12.12, s_1=3.56, \bar x_2=15.71, s_2=3.32$)
<br/>

**The 95% confidence interval is from ... to ...**

First, we need to get the data from the question
```{r}
fraud <- c(13.5, 12.6, 16.7, 6.7, 8.4, 16.3, 13.3, 14.3, 12.2, 7.2)
firearms <- c(16.4, 10.2, 16.2, 12.4, 17.5, 16.7, 17.6, 17.9, 20.8, 11.4)
```

The note means that these data are optional to know. In the case that the question does not provide these data, we could find sample mean, sample standard deviation, and size by running

Round to two decimal places
```{r}
round(mean(fraud), 2)
round(sd(fraud), 2)
length(fraud)
round(mean(firearms), 2)
round(sd(firearms),2)
length(firearms)
```

**We have the same data set with the note from the question, we could use the same approach in question 10.2.41 to find confidence interval **

**or we could use t.test() function in R to find confidence interval**

Since this is a pooled t-test, we specify var.equal = TRUE
```{r}
t.test(fraud, firearms, conf.level=.95, var.equal = TRUE)
```
To have 3 decimal places, we can use print() command
```{r}
print(t.test(fraud, firearms, conf.level=.95, var.equal = TRUE), 3)
```

**To illustate that we will have the same answer when we use the same approach in question 10.2.41**

First, we need to get the data from the question
```{r}
x1 = 12.12
s1 = 3.56
n1 = 10
x2 = 15.71
s2 = 3.32
n2 = 10
```
<hr />
This is a pooled t-test, to compute pooled sample standard deviation we use the formula 
$s_p= \frac{(n_1-1)s_1^2+(n_2-1)s_2^2}{n_1+n_2-2}$
```{r}
sp = sqrt( ( (n1-1)*s1^2 + (n2-1)*s2^2 )/ (n1+n2-2) )
sp
```

We need to find degree of freedom
```{r}
deg = n1+n2-2
```
Since the confidence level = 0.95, $\alpha = 1-.95=.05$To find $t_{\alpha/2}$ we run
```{r}
alpha = .05
t_alpha2 = abs(qt(alpha/2,deg))
t_alpha2
```

<br/>
**The 95% confidence interval is from... to...​(Round to three decimal places as​ needed.)**

To find confidence interval we use the formular $(\bar x_1 - \bar x_2) \pm t_{\alpha/2}.s_p\sqrt{1/n_1+1/n_2}$

```{r}
(x1-x2) - t_alpha2*sp*sqrt(1/n1+1/n2)
(x1-x2) + t_alpha2*sp*sqrt(1/n1+1/n2)
```
Round to three decimal places
```{r}
round((x1-x2) - t_alpha2*sp*sqrt(1/n1+1/n2),3)
round((x1-x2) + t_alpha2*sp*sqrt(1/n1+1/n2),3)
```
We finish a lot of complicated work by using R
<hr />
**Hope that helps!**