---
title: "13.5.103"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 13.2.18

Perform a​ chi-square homogeneity test. An independent simple random sample of residents in three regions gave the data on race shown in the table. At the 1 % significance​ level, do the data provide sufficient evidence to conclude that a difference exists in race distributions among the three​ regions?

<br/>
<hr/>
**Name of variables**

* row total: rTotal

* column total: cTotal

* total numbers of data: total

* original data: dframe1

* expected frequencies data: dframe2 
<hr/>

**What are the null and alternative​ hypotheses?**

Since the question asks "that a difference exists in race distributions among the three​ regions", the correct hypothesis is 

$H_0:$ The racial distribution is the same in each of the three regions.

$H_a:$ The racial distribution is not the same in each of the three regions.

**Find the test statistic.,$\chi^2$**

First we need to get the data from the question. (We can import it from Excel)
```{r}
data <- read.csv("~/R/Chapter 2/13.5.103/13.5.103.csv")
data
```
We store data into 2 different frame. The first one shows original data. The second shows expected frequency.
```{r}
dframe1 = data.frame(data)
dframe2 = data.frame(data)
```
<hr/>
Conditions to run a chi-square test

* All expected frequencies are 1 or greater

* At most 20% of the expected frequencies are less than 5

* The sample is a simple random sample

* The sample is an independent sample
<hr/>
**First approach: using chisq() in R which professor Covert introduces in the video lectures.(Recommended)**

**This approach is cleaner and faster**

First we need to create a new data frame which does not contain a column of names so our data frame only contains data. 

We can use subset to drop column of name.
```{r}
dframe3 = subset(dframe1, select = -c(X.))
dframe3
```
To see the difference between dframe1 and dframe3, we can run
```{r}
dframe1
```
We run chisq.test()
```{r}
chisq.test(dframe3, correct=FALSE)
```
Since df = 4, to find critical value for $\alpha = .01$
```{r}
alpha = .01
round(qchisq(1- alpha,4),3)
```
Since $\chi^2$ is right-tailed test by nature, our test statistic does not lie in rejected region 7.282 < 13.277 , we do not have enough evidence to reject the hypothesis
<hr/>
**If the question ask about expected frequencies, we can find it by running**
```{r}
chisq.test(dframe3, correct=FALSE)$expected
```
<hr/>
**Second approach using formular**

First we need to find row total and column total.
```{r}
cTotal = rep(0, nrow(dframe2))
rTotal = c()
for (i in 2:ncol(dframe2)){
  cTotal = cTotal + dframe2[,i]
  rTotal = c(rTotal, sum(dframe2[,i]))
}
total = sum(cTotal)
```

```{r}
cTotal
rTotal
total
```
We can find the test statistic $\chi^2$ by using the formula 
$\chi^2=\sum{\frac{(O-E)^2}{E}}$
```{r}
for (i in 2:ncol(dframe2)){
  dframe2[,i] <- sum(dframe2[,i])*cTotal/total
  print(dframe2[,i])
}
dframe2
```
**Find the test statistic.,$\chi^2$**
```{r}
chi = 0
for (i in 2:ncol(dframe2)){
  chi = chi + sum((dframe1[,i]-dframe2[,i])^2/dframe2[,i])
}
chi
```
Round to  three decimal places 
```{r}
round(chi,3)
```
**Find the critical value.$\chi_{\alpha}^2$**

We find degree of freedom by using the formula $df=(r-1)(c-1)$

Since dframe2 has 4 variables and the first one is x, so ncol(dframe2) returns 1 more than actual value. We find degree of freedom by running
```{r}
df = (ncol(dframe2)-2) * (nrow(dframe2)-1)
df
```
Our significant level is 1%, so $\alpha = .01$
```{r}
alpha = .01
round(qchisq(1- alpha,df),3)
```
Since $\chi^2$ is right-tailed test by nature, our test statistic does not lie in rejected region 7.282 < 13.277 , we do not have enough evidence to reject the hypothesis
<hr/>
**Hope that helps!**